---
title: "Developing Data Products Course Project"
author: "Ankitha Giridhar"
date: "15/11/2021"
output: ioslides_presentation
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This is the final work for the Developing Data Products Course Project. This includes a Shiny app and its associated documentation. In this project, multiple datasets corresponding to US States were used, including state.name, state.abb, state.division, state.region, state.center, state.area

## Links

The link to the app is: https://github.com/AnkithaGiridhar/Developing-Data-Products-Course-Project <br/>
The link to the source code is: https://ankithagiridhar.shinyapps.io/developing-data-products-course-project/

## About the Application

The app explores data about states in the USA. Upon selecting the state from the drop-down menu, the associated data is displayed in the main panel. The data includes the state code, division, region, area, and the latitude and longitude of the state's geographical center.

## Calculations
The calculations done display the average state area for the region of the selected state. For example, if the state of Pennsylvania is selected, the code implements:
```{r example}
mean(state.area[which(state.region==state.region[
  which(state.name=="Pennsylvania")])])
```

As observed, this code returns the average area of the states that share the same region as Pennsylvania.